Models

### 2023-02-21 Code/Models.Rmd
Fixed clusrank tests

```{r}
simulation <- function(model, base){
  simfit <- function(model, n = 12000000) {
    vc <- as.data.frame(VarCorr(model))
    ## mu <- exp(coef(model)$Year[,]) ## using fitted random effects only
    z <- rnorm(n, sd = vc$sdcor[1]) #$ using generated random effects
    mu <- exp(fixef(model) + z)
    shape <- 1 / vc$vcov[2]
    x <- rgamma(n, shape = shape, scale = mu / shape)
    x
  }
  sbase <- summary(base)
  #print(sbase)
  x <- simfit(model)
  print(mean(x < 0.1))
  print(quantile(x, prob = c(.00001, .0001, .0005, .001)))
  ## compare with and without random effect
  plot(density(x)) # with random effect
  curve(dgamma(x, shape = 1 / sbase$dispersion, 
               scale = exp(coef(base)) * sbase$dispersion), 
        0.08, 0.22, add = TRUE, col = "blue") # fixed effect only
}
simulation(old_pooled_year_gamma_log, old_pooled_one_gamma_log)
```

@@

##2019 vs 2022 Comparisons
```{r}
comp <- read.csv("../Data/Clusrank2019vs2022.csv")
#"C:\Users\ofior\Documents\Thesis\Data\2019vs2022.csv"
colnames(comp) <- c("Time", "Group", "Cluster")
#View(comp)
```

```{r}
library(clusrank)
#t.test(comp$NineteenH, comp$TwentyTwoH, paired = TRUE)
clusWilcox.test(comp$Time, group=comp$Group, cluster=comp$Cluster, paired = TRUE, alternative = "greater", method = "ds")
clusWilcox.test(comp$Time, group=comp$Cluster, cluster = comp$Group, paired = TRUE, alternative = "greater", method = "rgl")
clusWilcox.test(comp$Time, cluster = comp$Group, paired = TRUE, alternative = "greater", method = "ds")
#wilcox.test(comp$NineteenH, comp$TwentyTwoH, paired = TRUE)
```

@@

```{r}
library(clusrank)
#t.test(nations$NatH, nations$WorldH, paired = TRUE)
clusWilcox.test(nations$Time, group=nations$Group, cluster=nations$Cluster,
                paired = TRUE, alternative = "greater", method = "ds")
clusWilcox.test(nations$Time, group=nations$Cluster, cluster = nations$Group, 
                paired = TRUE, alternative = "greater", method = "ds")
#wilcox.test(nations$NatH, nations$WorldH, paired = TRUE)
```

>>>>

```{r}
set.seed(1)
simulation <- function(model, base){
  simfit <- function(model, n = 12000000) {
    vc <- as.data.frame(VarCorr(model))
    ## mu <- exp(coef(model)$Year[,]) ## using fitted random effects only
    z <- rnorm(n, sd = vc$sdcor[1]) #$ using generated random effects
    mu <- exp(fixef(model) + z)
    shape <- 1 / vc$vcov[2]
    x <- rgamma(n, shape = shape, scale = mu / shape)
    x
  }
  sbase <- summary(base)
  #print(sbase)
  x <- simfit(model)
  print(mean(x < 0.1))
  print(quantile(x, prob = c(.00001, .0001, .0005, .001)))
  ## compare with and without random effect
  plot(density(x)) # with random effect
  curve(dgamma(x, shape = 1 / sbase$dispersion, 
               scale = exp(coef(base)) * sbase$dispersion), 
        0.08, 0.22, add = TRUE, col = "blue") # fixed effect only
}
simulation(men_finals_year_gamma_log, men_finals_one_gamma_log)
```

@@

##2019 vs 2022 Comparisons
```{r}
comp <- read.csv("../Data/Clusrank2019vs2022.csv")
#"C:\Users\ofior\Documents\Thesis\Data\2019vs2022.csv"
colnames(comp) <- c("Time", "Athlete", "Year")
#View(comp)
```

```{r}
library(clusrank)
#t.test(comp$NineteenH, comp$TwentyTwoH, paired = TRUE)
#clusWilcox.test(comp$Time, group=comp$Group, cluster=comp$Cluster, paired = TRUE, alternative = "greater", method = "ds")
clusWilcox.test(Time, group=Year, cluster = Athlete, paired = TRUE, alternative = "greater", method = "ds", data = comp)
clusWilcox.test(Time, cluster = Athlete, paired = TRUE, alternative = "greater", method = "rgl", data = comp)
#wilcox.test(comp$NineteenH, comp$TwentyTwoH, paired = TRUE)
```

@@

```{r}
library(clusrank)
#t.test(nations$NatH, nations$WorldH, paired = TRUE)
#clusWilcox.test(nations$Time, group=nations$Group, cluster=nations$Cluster,
                #paired = TRUE, alternative = "greater", method = "ds")
clusWilcox.test(nations$Time, group=nations$Cluster, cluster = nations$Group, 
                paired = TRUE, alternative = "greater", method = "ds")
#wilcox.test(nations$NatH, nations$WorldH, paired = TRUE)
```
